---
title: "LF2649 HW01"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

#Import data
```{r}
hw1 = 
  read_csv("./da_ILINet.csv") %>% 
  janitor::clean_names()

head(hw1)
```

#Question 1

##1.1 What variables does the dataset contain?  How many weeks are included for each variable in the dataset? 
```{r}
colnames(hw1)
ncol(hw1)
nrow(hw1)

```

* This dataset contains `r ncol(hw1)` variables of `r colnames(hw1)`. 
* `r nrow(hw1)` weeks have been included for each variable.

##1.2 What state are you from? What was the ILI in the 2nd week of the season for your state?
```{r}
hw1 %>% 
  select("date", "new_york_city") %>% 
  filter(date == "2018-10-07") 

```

* I am from ourside of the USA.
* The ILI in the 2nd week of the season in NYC is 1931. 

##1.3 Suppose you store the dataset in a variable called ‘ili’.  What do the outputs from the following commands represent? 
```{r}
ili = hw1
a = ili[2, 6]  
# A represents the ILI in California on the 2nd week.

b = hw1 [30, 5:14]
colnames(b)
# B represents the 30th week ILI in Arkansas, California, Colorado, Connecticut, Delaware, District of Columbia, Florida, Georgia, Hawaii, and Idaho. 

c = ili [, 5]
# C represents ILI in the whole season in Arkansas. 

d = ili [36, "new_york_city"] 
# D represents the ILI in NYC on the 36th week. 
```


##1.4 What are the mean and maximum ILI levels for New York City, respectively? [hint: you can use the ‘summary’ function to print the summary statistics for each column. Or use the function 'mean' and 'max' to get the results respectively.]
```{r}
hw1 %>% 
  select("date", "new_york_city") %>% 
  summary()

```
* The mean and maximum ILI levels for New York City are 2290 and 4383, respectively. 

##1.5 When did New York City have its peak ILI (i.e. maximum ILI) that flu season?
```{r}
hw1 %>% 
  select("date", "new_york_city") %>% 
  filter(new_york_city == 4383)
```
* NYC had its peak ILI on 12/23/2018. 



#Question 2
## Plot the weekly ILI in New York City (column: New.York.City) over time.  (0.5pt) 
```{r}
weekly_nyc_plot = hw1 %>% 
  select(date, new_york_city) %>% 
  ggplot(aes(x = date, y = new_york_city)) + 
  geom_smooth(se = FALSE) 

weekly_nyc_plot
  
```

#Question 3
##New York City is in New York State. To compare ILI in NYC to that in NY State, superimpose the weekly ILI for NY State to the above plot (Q2). 
```{r}
hw1_tidy = 
  hw1 %>% 
  pivot_longer(
    alabama:wyoming, 
    names_to = "state",  
    values_to = "ili") 

nyc_ny_plot = 
  hw1_tidy %>% 
  filter(state %in% c("new_york", "new_york_city")) %>% 
  ggplot(aes(x = date, y = ili, color = state)) + 
  geom_smooth(se = FALSE)
  
nyc_ny_plot
```

#Question 4
##Use boxplot to show the variation in ILI among all states/cities for each week in the last flu season. [hint: think of each week as a category, and each with ~54 data points for all the states/cities.] (0.5pt)
```{r}
weekly_box = 
  hw1_tidy %>% 
  mutate(date = as.character(date)) %>% 
  ggplot(aes(x = date, y = ili)) + 
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

weekly_box
```

#Question 5
##Write a script in R to find the solutions for the following equations: (0.5pt)
```{r}
#a. 2x^2 + 10x + 3 = 0;
delta_a = sqrt(10^2 - 4*2*3)
x_a1 = (-10+delta_a)/2*2
x_a2 = (-10-delta_a)/2*2

#b. 5x^2 - 6x + 1 = 0;
delta_b = sqrt(6^2 - 4*5*1)
x_b1 = (6+delta_a)/2*5
x_b2 = (6-delta_a)/2*5

```

* The solutions for equation a are `r x_a1` and `r x_a2`.
* The solutions for equation b are `r x_b1` and `r x_b2`.

#Question 6
##To make implementation of Question 5 easier, create a function to find the solutions for any quadratic equation with constants a, b, and c.
```{r}
fn_sol_quadratic = function(a,b,c){
  
  delta = sqrt(b^2 - 4*a*c)
  x_1 = (-b + delta)/2*a
  x_2 = (-b - delta)/2*a
  
  return(slt = c(x_1, x_2))
  
}

q5 = fn_sol_quadratic(2,10,3)
q5

```
* We get the function as "fn_sol_quadratic".  
